Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-11 paper/main.tex
revising text/comments: into, methods, results

\begin{itemize}
    \item in case the additional contrast stay in supplemental material, just
        speak of contrast not ``primary contrast''
    \item in main text, add references to supplemental material
    \item there is no "cue about" in the English language? Alternatives are
        "give a hint on/about", "indicate"; changed the sentences but should
        ask Alex
\end{itemize}

@@

\begin{itemize}
    \item Figure of regressor correlations: maybe write out in full the name of
        regressors (instead of pointing to the table)
\end{itemize}

@@

% irrespective of visual content
Notably, categorization was performed irrespectively of a movie frame's precise
content and thus without controlling confounding variables.
% AV COPEs: intro
The rationale that this approach would yield categories that - on average - show
different stimulus features.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movie shots tend to establish the setting
(\texttt{vse\_new}) and the spatial relationships within a setting
(\texttt{vpe\_new}) at the beginning of a movie.
% cut to recurrent scene
Later in the movie, the field sizes of movie shots tend to decrease when
switching back to already established settings (\texttt{vse\_old}).
% similarly for shots within a scene
Later in the movie when the spatial layout of a setting is already established,
shots within a setting shift to objects more relevant to the evolved plot and or
to switching between faces of persons talking to each others (\texttt{vpe\_old})
\citep{brown2012cinematography, mercado2011filmmakers}.
% neuroscientific rationale
The neuroscientific rationale was that activity in the PPA is greater when
participants view novel versus repeated scenes or view-points
\citep{epstein1999parahippocampal, grill2006repetition}.
%
\todo{imo its better to focus on the cinematographic rationale and drop the last
sentence 'cause activity in e.g. FFA adopts too -> we might substract an on
average smaller response}
% no cut condition: intro
In order to create a control condition, a sixth category (\texttt{no\_cut}) was
created by pseudo-randomly drawing movie frames from continuous movie shots that
lasted longer than \unit[20]{s}.
% no cuts: how
Events were drawn from movie shots in such a way that each event had a minimum
temporal distance of at least \unit[10]{s} to a movie cut and to another
\texttt{no\_cut} event.

@@

\begin{figure*}[h!]
\centering
    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
        correlation coefficients of the regressors used in the analysis of the
        audio-description (blue; see Table \ref{tab:ao-events} for a
        description) and audio-visual movie (red; see Table \ref{tab:av-events})
        rounded to the nearest tenth.
        The correlation between the two stimuli's
        root mean square loudness and between their left-right difference in
        loudness yielded the highest correlation values
        (\texttt{fg\_ad\_rms} and \texttt{fg\_av\_ger\_rms}, r=.7635;
        \texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749).
        \todo[inline]{not all labels are actually listed in that table; which
        ones are not listed? checked it, all labels listed}
      }
\label{fig:reg-corr}
\end{figure*}

@@

\todo[inline]{COH: tried to make clear why we did not/could not use ``places vs.
faces''}

@@

spatial information compared to the perception of ``non-spatial'' information

@@

activity in the PPA.
% but we expect differences because
Nevertheless, we also assumed contrasts would differ in [?] \todo{differ in
what?  ``localization performance'' isn't well phrased. How ``well'', ``nice''
the results are?} since the event categories differed a) in how well the
averaged events reflected spatial information, and b) in available data (i.e.
event counts).
Notably, localization of the PPA in individual subjects that was done by
\citep{sengupta2016extension} using the established approach of contrasting
blocks of pictures is based on one contrast for each subjects (cf. Table 3 in
\citep{sengupta2016extension}) that was chosen post-hoc from a set of three
contrasts (\textit{strict}, \textit{relaxed}, and \textit{simple} contrast
\citep{sengupta2016extension}).
% thus: primary contrasts
Here, we chose one contrast to be ``primary contrast'' for later detailed
inspection and report.

@@

subjectively good balance between a) the amount of available data, b) how
well the average of events within represented spatial information and
non-spatial information respectively (cf. section \ref{rationale}).

@@

was not depicted before (\texttt{vse\_new}) to cuts that we accompanied with a
change of the camera position within a setting that was already occurring
previously (\texttt{vpe\_old}).

@@

\texttt{geo}, and rooms and geometry-defining objects \texttt{geo-room} with all
non-geometry related categories (\texttt{body}, \texttt{bodypart},
\texttt{fahead}, \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}) except
\texttt{furniture} to get a sufficient amount of events per stimulus segment.
\todo[inline]{in detail: \texttt{fahead}: just N=83; mostly parts
 of face (``ear'', ``nose''), or vague description (``his/her face''; N=10)}

@@

% hierarchical categories
[c) the narrator is often lacking behind a short dialogue or a change of the
soundscape that might already indicate a change of settings.] \todo[inline]{for
sake of conciseness, it is imo better to drop that ``soundscape-thing''}

@@

\todo[inline]{it's probally not about the soundscape anymore (to speculative)
but about the somewhat correlation of nouns and cuts}

@@

\todo[inline]{SE: in Figure weiter reinoomen; bei FFA/PPA etc sind
flatmaps/inflated brains standard; COH: imo it is important that we do not have
clusters all over the brain}

@@

% Sengupta et al., 2016
The visual localizer \citep{sengupta2016extension} yielded bilateral
parahippocampal clusters in 12 of 14 subjects and an unilateral right clusters
in two subjects (sub-04, sub-20).\todo{I shortened the following part (maybe too
much)}
% Sengupta: 1 of 3
Individual PPAs were assessed by visually inspecting unthresholded $t$-maps
(Z>1.64, p<.05 cluster corrected)  of three different $t$-contrasts
(\textit{strict}, \textit{relaxed}, and \textit{simple} stimulus set cf.
\citep{sengupta2016extension}), and titrating [?] the $t$-threshold in the range
of [2, 3] in until we found an isolated cluster that matched the expected
anatomical location based on literature \citep{epstein1998ppa}.
\todo{they used $t$-maps???}
% one contrast to localize them all; "...and Z>3.4 for all"
Contrary to \citep{sengupta2016extension}, we here used the same contrast of
each naturalistic stimulus and the same threshold for all subjects (Z>2.3, p<.05
cluster-corrected for the analysis in subject-space; Z>3.4, p<.05 for the
analysis in group-space).
% subject space -> NeuroVault
Results of the analyses that were performed in subject-space can be found in the
accompanying dataset.
% here report in group space
For better comparisons of subjects, we here report results from the analyses
performed in group space.
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AV
and AD $t$-contrast, and the outline of overlapped, individual PPAs
\citep{sengupta2016extension} co-registed to the MNI152 template.
% one slice to show them all
Transversal slice of z=-11 was chosen as it depicts [at least some] voxels of
significant clusters in almost all subjects.

>>>>

\begin{itemize}
    \item speaking of "primary contrast" probably not necessary anymore.
    \item main text: add references to supplemental material
\end{itemize}

@@

\begin{itemize}
    \item Fig regressor correlations: maybe write out in full the name of
        regressors (instead of pointing to the table)
\end{itemize}

@@

% irrespective of visual content
Notably, categorization was performed irrespectively of a movie frame's precise
content and thus without controlling confounding variables.
% AV COPEs: intro
The rationale that this approach would yield categories that - on average - show
different stimulus features.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movie shots tend to establish the setting
(\texttt{vse\_new}) and the spatial relationships within a setting
(\texttt{vpe\_new}) at the beginning of a movie.
% cut to recurrent scene
Later in the movie, the field sizes of movie shots tend to decrease when
switching back to already established settings (\texttt{vse\_old}).
% similarly for shots within a scene
Later in the movie when the spatial layout of a setting is already established,
shots within a setting shift to objects more relevant to the evolved plot and or
to switching between faces of persons talking to each others (\texttt{vpe\_old})
\citep{brown2012cinematography, mercado2011filmmakers}.
% neuroscientific rationale
The neuroscientific rationale was that activity in the PPA is greater when
participants view novel versus repeated scenes or view-points
\citep{epstein1999parahippocampal, grill2006repetition}.
%
\todo{better focus on cinematographic rationale \& drop last sentence; activity
in e.g. FFA adopts too -> we might substract an on average smaller response}
% no cut condition: intro
In order to create a control condition, a sixth category (\texttt{no\_cut}) was
created by pseudo-randomly drawing movie frames from continuous movie shots that
lasted longer than \unit[20]{s}.
% no cuts: how
Events were drawn from movie shots in such a way that each event had a minimum
temporal distance of at least \unit[10]{s} to a movie cut and to another
\texttt{no\_cut} event.

@@

\begin{figure*}[h!]
\centering
    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
        correlation coefficients of the regressors used in the analysis of the
        audio-description (blue; see Table \ref{tab:ao-events} for a
        description) and audio-visual movie (red; see Table \ref{tab:av-events})
        rounded to the nearest tenth.
        The correlation between the two stimuli's
        root mean square loudness and between their left-right difference in
        loudness yielded the highest correlation values
        (\texttt{fg\_ad\_rms} and \texttt{fg\_av\_ger\_rms}, r=.7635;
        \texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749).
        \todo[inline]{checked it, all labels listed}
      }
\label{fig:reg-corr}
\end{figure*}

@@

@@

spatial information compared to the perception of non-spatial information

@@

activity in the PPA but chose one contrast to be the ``primary contrast'' for
later detailed inspection and report.

@@

subjectively good balance between a) how well the average of events within
categories represented spatial information and non-spatial information
respectively (cf. section \ref{rationale}), and b) the amount of available data.

@@

was not depicted before (\texttt{vse\_new}) to cuts merely switching the camera
position within a setting that was already established earlier in the movie
(\texttt{vpe\_old}).

@@

\texttt{geo}, and rooms and geometry-defining objects \texttt{geo-room} with not
just nouns referring to a person's head or face (\texttt{fahead}, N=83; e.g.
``eyes'', ``face'', or ``head'') but also all non-geometry related categories
(\texttt{body}, \texttt{bodypart}, \texttt{fahead}, \texttt{object},
\texttt{sex\_f}, \texttt{sex\_m}) except \texttt{furniture} to get more events
per stimulus segment.

@@

% c) the narrator is often lacking behind a short dialogue or a change of the
% soundscape that might already indicate a change of settings.

@@

In the VIS study \citep{sengupta2016extension} using the established approach of
contrasting blocks of pictures, assessment of individual PPAs was based on
chosing post-hoc one from a set of three contrasts (\textit{strict},
\textit{relaxed}, and \textit{simple} contrast \citep{sengupta2016extension};
cf. Table 3 in \citep{sengupta2016extension}).

@@

@@

% Sengupta et al., 2016
The visual localizer \citep{sengupta2016extension} yielded bilateral
parahippocampal clusters in 12 of 14 subjects and an unilateral right clusters
in two subjects (sub-04, sub-20).
% Sengupta: 1 of 3
Individual PPAs were assessed by visually inspecting unthresholded $t$-maps
(Z>1.64, p<.05 cluster corrected)  of three different $t$-contrasts
(\textit{strict}, \textit{relaxed}, and \textit{simple} stimulus set cf.
\citep{sengupta2016extension}), and titrating [?] the $t$-threshold in the range
of [2, 3] in until we found an isolated cluster that matched the expected
anatomical location based on literature \citep{epstein1998ppa}.
\todo{they used $t$-maps???}
% one contrast to localize them all; "...and Z>3.4 for all"
Contrary to \citep{sengupta2016extension}, we here used the same contrast of
each naturalistic stimulus and the same threshold for all subjects (Z>2.3, p<.05
cluster-corrected for the analysis in subject-space; Z>3.4, p<.05 for the
analysis in group-space).
% subject space -> NeuroVault
Results of the analyses that were performed in subject-space can be found in the
accompanying dataset.
% here report in group space
For better comparisons of subjects, we here report results from the analyses
performed in group space.
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AV
and AD $t$-contrast, and the outline of overlapped, individual PPAs
\citep{sengupta2016extension} co-registed to the MNI152 template.
% one slice to show them all
Transversal slice of z=-11 was chosen as it depicts [at least some] voxels of
significant clusters in almost all subjects.
